### 2016-06-29 publications/Journal/1-introduction.tex
Added reference to another paper
Added some more references to papers

But with the ever increasing complexity of simulation models, parallel simulation becomes necessary to perform the simulation within reasonable time bounds.
Whereas \textsf{Parallel DEVS}~\cite{ParallelDEVS} was introduced to increase parallelism, its inherent parallelism is often insufficient.
Several synchronization protocols from the discrete event simulation community~\cite{FujimotoBook} have been applied to \textsf{DEVS} simulation~\cite{globaltimewarp}.
Through synchronization protocols, different simulation cores can be at different points in simulated time, increasing parallelism significantly, at the cost of synchronization overhead.
While several parallel \textsf{DEVS} simulation kernels exist, they are often limited to a single synchronization protocol.
The reason for different synchronization protocols, however, is that their distinct nature makes them applicable in different situations, each outperforming the other in specific models.
The applicability of parallel simulation capabilities of current tools is therefore constrained to specific domains.

>>>>

But with the ever increasing complexity of simulation models, parallel simulation becomes necessary to perform the simulation within reasonable time bounds.
Whereas \textsf{Parallel DEVS}~\cite{ParallelDEVS} was introduced to increase parallelism, its inherent parallelism is often insufficient~\cite{Himmelspach}.
Several synchronization protocols from the discrete event simulation community~\cite{FujimotoBook} have been applied to \textsf{DEVS} simulation~\cite{globaltimewarp}.
Through synchronization protocols, different simulation cores can be at different points in simulated time, increasing parallelism significantly, at the cost of synchronization overhead.
While several parallel \textsf{DEVS} simulation kernels exist, they are often limited to a single synchronization protocol.
The reason for different synchronization protocols, however, is that their distinct nature makes them applicable in different situations, each outperforming the other in specific models~\cite{Jafer}.
The applicability of parallel simulation capabilities of current tools is therefore constrained to specific domains.
